Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.9)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-30 results.tex
Changed the description of simonettas model

\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.

>>>>

\blue{The dash-dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not well described.

### 2011-03-30 summary.tex
Changed the description of simonettas model

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. \blue{The other model fit~\cite{Liu11} does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data as accurately. A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points~\cite{Gui11}. The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005. The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.

>>>>

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. \blue{The other model fit~\cite{Liu11} does not include the H{\sc ermes} data from 1996-2005 and describes the $t$-projection of the $A^{\sin\phi}_{\textrm{LU}}$ well. A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points~\cite{Gui11}. The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005. The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.
